Peaks Over Threshold for Bursty Time Series

### 2018-04-24 article_springer/article_springer.Rmd
add something about cluster of extremes

When we introduced the CTRE model, we assumed that all events are i.i.d. 
This assumption is likely sufficient but not necessary for our limit theorem to hold. 
Morevoer, any data below a (minimum) threshold $\ell_0$ is discarded in 
our inference procedure, and hence need not satisfy the i.i.d. assumption.
For the purposes of statistical inference, we merely require that the 
inter-threshold-crossing times are i.i.d.

>>>>

When we introduced the CTRE model, we assumed that all events are i.i.d. 
This assumption is likely sufficient but not necessary for our limit theorem to hold. 
Moreover, any data below a (minimum) threshold $\ell_0$ is discarded in 
our inference procedure, and hence need not satisfy the i.i.d. assumption.
For the purposes of statistical inference, we merely require that the 
inter-threshold-crossing times are i.i.d. However, it might be interesting 
to generalize our theory to the case of a stationary sequence of magnitudes. In case of fixed times between observations, the distribution of the sequence of (correctly normalized) inter-exceedance times converges under certain (mixing) conditions to a mixture of an exponential distribution and a point mass in zero [@ferro2003inference]. Hence, this also leads to a model for extreme events that occur in cluster. Allowing for both, dependence between the magnitudes and heavy tailed waiting times, could maybe further improve modelling of extreme events like earthquakes, that occur in clusters.
